---
title: "Restore Project Environment"
format: html
---

This document will help you restore the project environment using `renv`. It will:

1. Check if renv is installed
2. Install renv if needed
3. Restore the project environment from renv.lock

## Check and Install renv

```{r}
#| warning: false
#| message: false

# Function to check and install renv
setup_renv <- function() {
  if (!require("renv", quietly = TRUE)) {
    cat("renv is not installed. Installing it now...\n")
    install.packages("renv", repos = "https://cloud.r-project.org")
  }
  library(renv)
  cat("renv is ready!\n")
}

# Run the setup
setup_renv()
```

## Restore Project Environment

```{r}
#| warning: false
#| message: false

# Restore the project environment
cat("Restoring project environment from renv.lock...\n")
renv::restore()
```

## Verify Installation

Let's verify that the key packages are available:

```{r}
#| warning: false
#| message: false

# Function to check if a package is installed
check_package <- function(pkg_name) {
  if (require(pkg_name, character.only = TRUE, quietly = TRUE)) {
    cat(sprintf("✓ %s is installed and loaded\n", pkg_name))
  } else {
    cat(sprintf("✗ %s is NOT installed properly\n", pkg_name))
  }
}

# Check our main packages
check_package("tidyverse")
check_package("palmerpenguins")
```

## Next Steps

If all packages were restored successfully:

1. You can now run any of the project's Quarto documents
2. All required packages should be available
3. Your environment matches the project's specifications

If you encounter any issues:

1. Check that R is up to date
2. Make sure you have write permissions in the project directory
3. Look for any error messages in the output above 