---
title: "Project Setup with renv"
format: html
---

## Project Environment Setup

This document will set up the R environment for this project using `renv`. It will:

1. Initialize renv for package management
2. Install required packages
3. Create a snapshot of the environment

### Phase 1: Initialize renv

```{r}
#| warning: false
#| message: false

# Phase 1: Initialize renv
init_renv <- function() {
  # Install renv if not already installed
  if (!require("renv")) {
    install.packages("renv")
  }
  
  # Load renv
  library(renv)
  
  # Check if renv is already initialized (look for renv.lock)
  if (!file.exists("renv.lock")) {
    # If no lockfile exists, initialize renv
    cat("Initializing new renv project...\n")
    renv::init(force = TRUE)
  } else {
    # If lockfile exists, just activate
    cat("Project already initialized. Activating renv...\n")
    renv::activate()
  }
}

# Run initialization
init_renv()
```

### Phase 2: Install Packages

```{r}
#| warning: false
#| message: false

  # Take a snapshot of the current project state
  renv::snapshot(force = TRUE)
  
```


## Next Steps

The environment is now set up! Other users can:

1. Clone this project
2. Open it in RStudio or their preferred R environment
3. Run `renv::restore()` to install all packages at the exact versions used here
4. Start working with the same environment setup 